---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nwsrfsr

<!-- badges: start -->
<!-- badges: end -->

Provides functions to call Fortran versions of NWS operational 
hydrology models, Sacramento Soil Moisture Accounting (SAC-SMA), 
Snow Accumulation and Ablation (SNOW17). Also provides an 
interface to the unit hydrograph routing model. The Fortran code 
used in this package is considered "legacy" and is not supported,
but it should not have any significant differences from current 
operational models. 

## Installation

You can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("NOAA-NWRFC/nwsrfs-hydro-models", subdir = "nwsrfs_r")
```
## Example


```{r example}
library(nwsrfsr)

```

## Citation

Use the package-native citation metadata:

```r
citation("nwsrfsr")
```

This includes the software citation and the accepted 2026 JAWRA paper reference.

Repository-level citation metadata is available at:

- `/CITATION.cff` (repo root)

## Legal

- Package license: `LICENSE`
- Package notice: `NOTICE`
